|

### 2022-07-25 manuscript_BE/manuscript_BE.Rmd
Further changes to the manuscript

The model shows that agents need to find a way 
to incorporate future consequences of current choices. In the model, 
this could be achieved with either of two parameters that could 
also work together.  First, $\gamma$ measures how
much individuals include future rewards in their decision updates. 
If $\gamma=0$, individuals only use the immediate reward obtained from a
cleaning interaction. As $\gamma$ increases, individuals include more the
reward obtained from the subsequent choices. That amounts to estimating
and using for decision making the future expected rewards of an action (chaining).
Second, $\eta$ measures how much individuals include in their reward the
fleeing behavior of visitors as a negative component (penalty). Both of
these parameters allow individuals to use in their estimates the future
effects of their choices.

@@

The empirical data were collected between 2010 and 2019 always during 
the austral winter months June to August from a total of five 
study reef sites (Corner Beach-CB, Horseshoe-HS, Mermaid Cove-MC, 
Northern Horseshoe-NHS, and The Crest-TC)  at Lizard Island 
($14.6682^\circ S, 145.4604^\circ E$), Great Barrier Reef, Australia. 
The data consist of three sets: fish censuses, field 
observations of cleaner-client interactions to quantify the probability 
of visitors leaving if made to wait, and the 
performance of wild-caught cleaner fish in the ephemeral reward test. 
In total, we have twelve site/year data sets for fish censuses and 
corresponding performance in the lab test. Thus, some sites were sampled more 
than once. To estimate the population density of cleaner fish 
and their clients at a given site in 
a given year, @triki_Biological_2019 used a series of ten 
transects of $30m$ each. Observers swam along the transect lines placed on 
the reef and first counted the visible large-bodied adult fish 
(species with total length $TL \geq 10cm$) including cleaner fish 
on a width of $5m$, and then on the 
return individuals of small-bodied fish species ($TL < 10 cm$)
on a width of $1 m$
(see @triki_Decrease_2018 for further details on fish censuses data collection). 
We then scaled the counts of cleaner fish, small-bodied, 
and  large-bodied  clients fish densities per $100 m^2$. 
From the study by @triki_Biological_2019 
cleaner fish and large-bodied client populations densities were 
highly correlated, and only the former 
was hence used in the analyses as representative of both measures.

The field observation data consisted of video recordings/encodings of the 
cleaner-client cleaning interactions. There were videos from eight 
cleaners per site/year of a duration of $30 min$ each. Triki et al. 
extracted information from every event wherein a visitor client 
was made to wait in favour of another client (visitor or resident), and noted 
whether or not the visitor left or queued for the cleaning service
[@triki_Biological_2019;@triki_Brain_2020].

The cognitive performance data was from a total of 120 cleaners 
(10 individuals per 12 site/year) tested in the 
ephemeral reward task [@triki_Biological_2019;@triki_Brain_2020]. Authors 
housed all captured cleaners individually in glass aquaria 
($62cm \times 27cm \times 37 cm$) and provided them 
with PVC pipes ($10 cm \times 1 cm$) as shelters. 
The task consisted of exposing the cleaner fish to substitute 
models of client fish in the form of two *Plexiglas* plates offering the 
same amount of food (one item of mashed prawn).  The two plates differed 
in colour and pattern (horizontal green stripes or vertical pink stripes) 
but had equal size ($10 cm \times 7 cm$). Importantly, the two plates played 
different roles as either a visitor (ephemeral food source) or 
resident (permanent food source). That is, if a cleaner fish inspected the 
resident plate first, the experimenter withdrew the visitor plate out of 
the aquarium as a consequence.  Choosing first the visitor plate, 
however, granted access to both plates. The equal size of the plates 
forced cleaner fish to learn to give service priority to the visitor plate 
based solely on the behavior-cue of the plates rather than size-cue 
[@wismer_Cuebased_2019]. Triki et al. [-@triki_Biological_2019;@triki_Brain_2020] 
tested the fish for a maximum of 200 trials with 20 trials a day, 10 trials 
in the morning and 10 trials in the afternoon. They randomized and 
counterbalanced the plates’ spatial location (i.e. left or right) 
between trials. Similarly, they counterbalanced the plates’ decoration 
(colour and pattern) and the plates’ role (visitor or resident) between the 
tested fish. In the original studies, once a fish reach a learning criterion, 
that is, performing significantly above chance level ($> 50%$, $p-value ≥ 0.05$),
they passed to a reversal version of the task where the roles of the 
visitor/resident Plexiglas plates were swapped 
(see Triki et al.[-@triki_Biological_2019;@triki_Brain_2020]). 
Here, we used instead a subset of these data in order to have an idea of 
cleaner fish preferences for the visitor plate, even if they do not reach 
the learning criterion within 200 trials. To do so, we first extracted the 
trial-by-trial outcomes from the last two sessions (20 trials) of those who 
never reached the learning criterion for visitor plate 
($N = `r fieldData.cleaner.filt.sum[V1==2,length(V1)]`$ cleaner fish). 
For those who reached the learning criterion at some point during the 
test and passed to a reversal phase, we extracted the trial-by-trial 
outcomes from the last session (10 trials) before passing to reversal 
and the last 10 trials they were exposed to in the test 
($N = `r fieldData.cleaner.filt.sum[V1>2,length(V1)]`$ cleaner fish). 
We chose a combination of initial and reversal to quantify preference 
for the visitor client, given that it matches well the criteria chosen 
in previous analysis of the ephemeral reward task experimental set-up
[@triki_Biological_2019;@triki_Brain_2020]. In the 
supplementary material (Fig. \ref{fig:rawdata}) we show how our choice maps
to the previously used criteria. For comparison, we also show a quantification 
of visitor preference based only on the initial phase of the task.

@@

The aim of the analyses is to fit the key model parameters 
$\gamma$ and $\eta$, to the empirical data from Triki et al. 
[-@triki_Biological_2019;@triki_Brain_2020] to test whether each or 
a combination of these effects is a better explanation for the pattern 
seen in the data. We used the ecological variables: cleaners, visitor clients, 
resident clients abundances and visitor clients leaving probability,  
as input to the models. As the response variable, we used cleaners' 
preference for visitors over residents in the ephemeral reward task. 
Finally, we used the preference for visitors resulting from the 
model simulations as the prediction for the response variable. 
We kept all other parameter values used for the model simulations constant, 
see Table \ref{tab:param}.

@@

Once we calculated the relative abundances, we obtained predictions from 
the model for each one of the locations and ran the Markov Chain. We started the
chain with random values for the parameters of interest, then ran the 
computational model once for every reef site using as input the ecological 
explanatory variables. The model outputs the probability of choosing the visitor
for each location $p_i$, where $i$ is the index for the 12 locations. Assuming a 
binomial distribution, the probability that each of the cleaner fish 20 choices 
in the ephemeral reward task was generated by the model 
is given by $\binom{n}{k_ij}p^{k_{ij}}_i (1-p_i)^{n-k_{ij}}$;
where $k_{ij}$ is the number of times that cleaner fish $j$ in reef site $i$ 
chose the visitor over the resident; and $n=20$ (due to our choice of using 20 
choices per cleaner fish). By taking the natural logarithm and summing over all 
the cleaner fish and reef sites, we obtained the log-likelihood of the data 
given the model and parameters. We then proposed a new set of parameters drawn 
from a uniform distribution centred around the old parameter set. The amplitude 
of the uniform distribution used for each parameter can be found in Table 
\ref{tab:param}. Subsequently, we ran the model and calculated the likelihood 
with the new parameter set. We then used the ratio of the two likelihoods to 
choose which parameter set to keep. New parameter sets with a higher likelihood 
than the old set replaced old ones, and those with a lower likelihood replaced 
current ones  with a probability equal to the log-likelihood ratio. 
Given that we only used the likelihoods in the decision, we used an 
uninformative prior. Once we decided whether the new parameter set 
would replace the old one, we ran the model again to sample the likelihood 
distribution of the parameter set. We then started 
the cycle again by proposing a new set of parameters and repeated
the process for $1e^5$ steps. We ran 5 independent chains, 
discarded the first $1000$ samples of each chain as burn in, 
and after that, we kept 1 in every 100 samples to avoid autocorrelation. 
The collection of parameters sets kept in 
all chains approximates the posterior distribution. We coded the model 
as well as the fitting algorithm in *c++*, the diagnostics and visualization 
in R [@rcoreteam_Language_2021]. All codes are accessible at 
<DOI: 10.5281/zenodo.6338073>

@@

```{r rawdata,fig.cap='Relation between the response variable used in this study and the criteria used in previous studies to assess performance in the ephemeral reward task. In the x axis, we classified the performance of cleaner fish according to whether they developed a preference for the visitor in the initial round, in the initial and reversal, or none of them. In the y axis, we add the choices of two experimental sessions: panel on the left uses one session from the initial round and one from the reversal round when possible (as described in the main text); panel on the right uses two sessions from the initial round for all fish.',out.width='100%',fig.height=5,cache=FALSE}
plot_grid(initANDRev,init,ncol = 2)

>>>>

The model shows that agents need to find a way 
to incorporate future consequences of current choices. In the model, 
this could be achieved with either of two parameters that could 
also work together.  First, $\gamma$ measures how
much individuals include future rewards in their decision updates. 
If $\gamma=0$, individuals only use the immediate reward obtained from a
cleaning interaction. As $\gamma$ increases, individuals include more of the
reward obtained from the subsequent choices. That amounts to estimating
and using for decision making the future expected rewards of an action (chaining).
Second, $\eta$ measures how much individuals include in their reward the
fleeing behavior of visitors as a negative component (penalty). Both of
these parameters allow individuals to use in their estimates the future
effects of their choices.

@@

The empirical data were collected between 2010 and 2019 always during 
the austral winter months June to August from a total of five 
study reef sites (Corner Beach-CB, Horseshoe-HS, Mermaid Cove-MC, 
Northern Horseshoe-NHS, and The Crest-TC)  at Lizard Island 
($14.6682^\circ S, 145.4604^\circ E$), Great Barrier Reef, Australia. 
The data consist of three sets: fish censuses, field 
observations of cleaner-client interactions to quantify the probability 
of visitors leaving if made to wait, and the 
performance of wild-caught cleaner fish in the ephemeral reward test. 
In total, we have twelve site/year data sets for fish censuses and 
corresponding performance in the lab test. Thus, some sites were sampled more 
than once. To estimate the population density of cleaner fish 
and their clients at a given site in 
a given year, @triki_Biological_2019 used a series of ten 
transects of $30m$ each. Observers swam along the transect lines placed on 
the reef and first counted the visible large-bodied adult fish 
(species with total length $TL \geq 10cm$) including cleaner fish 
on a width of $5m$, and then on the 
return individuals of small-bodied fish species ($TL < 10 cm$)
on a width of $1 m$
(see @triki_Decrease_2018 for further details on fish censuses data collection). 
Total length estimates were done by the observer. 
We then scaled the counts of cleaner fish, small-bodied, 
and  large-bodied  clients fish densities per $100 m^2$.

The field observation data consisted of video recordings/encodings of the 
cleaner-client cleaning interactions. There were videos from eight 
cleaners per site/year of a duration of $30 min$ each. Triki et al. 
extracted information from every event wherein a visitor client 
was made to wait in favor of another client (visitor or resident), and noted 
whether or not the visitor left or queued for the cleaning service
[@triki_Biological_2019;@triki_Brain_2020].

The cognitive performance data was from a total of 120 cleaners 
(10 individuals per 12 site/year) tested in the 
ephemeral reward task [@triki_Biological_2019;@triki_Brain_2020]. Authors 
housed all captured cleaners individually in glass aquaria 
($62cm \times 27cm \times 37 cm$) and provided them 
with PVC pipes ($10 cm \times 1 cm$) as shelters. 
The task consisted of exposing the cleaner fish to substitute 
models of client fish in the form of two *Plexiglas* plates offering the 
same amount of food (one item of mashed prawn).  The two plates differed 
in colour and pattern (horizontal green stripes or vertical pink stripes) 
but had equal size ($10 cm \times 7 cm$). Importantly, the two plates played 
different roles as either a visitor (ephemeral food source) or 
resident (permanent food source). That is, if a cleaner fish inspected the 
resident plate first, the experimenter withdrew the visitor plate out of 
the aquarium as a consequence.  Choosing first the visitor plate, 
however, granted access to both plates. The equal size of the plates 
forced cleaner fish to decide based solely on the association between 
the behaviour and the collor/pattern cue [@wismer_Cuebased_2019]. 
Triki et al. [-@triki_Biological_2019;@triki_Brain_2020] 
tested the fish for a maximum of 200 trials with 20 trials a day, 10 trials 
in the morning and 10 trials in the afternoon. They randomized and 
counterbalanced the plates’ spatial location (i.e. left or right) 
between trials. Similarly, they counterbalanced the plates’ decoration 
(colour and pattern) and the plates’ role (visitor or resident) between the 
tested fish. In the original studies, once a fish reached a learning criterion, 
that is, performing significantly above chance level in a binomial test 
($p-value 	\leq 0.05$, ),
they passed to a reversal version of the task where the roles of the 
visitor/resident Plexiglas plates were swapped. The reversal phased 
stopped when the fish performed significatly above chance, or the fish
completed the 200 trial together with the initial;
see Triki et al.[-@triki_Biological_2019;@triki_Brain_2020]. 
Here, we are interested in explaining the total frequency of visitor choices
using the model, rather than just the achievement of the criterion. 
Total frequency of visitor choices naturally comes out of the model, 
and allows us to use all the variation among cleaners, instead of reducing 
that to a binomial variable.
Thus, we used instead a subset of these data to estimate the final 
cleaner fish preferences for the visitor plate, even if they do not reach 
the learning criterion within 200 trials. To do so, we first extracted the 
trial-by-trial outcomes from the last two sessions (20 trials) of those who 
never reached the learning criterion for visitor plate 
($N = `r fieldData.cleaner.filt.sum[V1==2,length(V1)]`$ cleaner fish). 
For those who reached the learning criterion at some point during the 
test and passed to a reversal phase, we extracted the trial-by-trial 
outcomes from the last session (10 trials) before passing to reversal 
and the last 10 trials they were exposed to in the test 
($N = `r fieldData.cleaner.filt.sum[V1>2,length(V1)]`$ cleaner fish).

We chose a combination of initial and reversal to quantify preference 
for the visitor client. However, it could be argued that using only the initial
phase gives a better estimation of the cleaner fish preference for the visitor. 
In the supplementary material (Fig. \ref{fig:rawdata}) we show how using 
initial and reversal (a), and only initial (b) maps
to the previously used criteria. The initial and reversal match better
the criteria chosen in previous analysis of the ephemeral 
reward task experimental set-up
[@triki_Biological_2019;@triki_Brain_2020].

@@

The aim of the analyses is to fit the key model parameters 
$\gamma$ and $\eta$, to the empirical data from Triki et al. 
[-@triki_Biological_2019;@triki_Brain_2020] to test whether each or 
a combination of these effects is a better explanation for the pattern 
seen in the data. We used the ecological variables: cleaners, visitor clients, 
resident clients abundances and visitor clients leaving probability,  
as input to the models. As the response variable, we used the frequency with 
which cleaners chose the visitor option in the ephemeral reward task. 
Finally, we used the probability with which agents in the model
simulations choose the visitor in resident-visitor options
as the prediction for the response variable. 
We kept all other parameter values used for 
the model simulations constant, see Table \ref{tab:param}.

@@

Once we calculated the relative abundances, we obtained predictions from 
the model for each one of the locations and ran the Markov Chain. We started the
chain with random values for the parameters of interest, then ran the 
computational model once for every reef site using as input the ecological 
explanatory variables. The model outputs the probability of choosing the visitor
for each location $p_i$, where $i$ is the index for the 12 locations. Assuming a 
binomial distribution, the probability that each of the cleaner fish 20 choices 
in the ephemeral reward task was generated by the model 
is given by $\binom{n}{k_ij}p^{k_{ij}}_i (1-p_i)^{n-k_{ij}}$;
where $k_{ij}$ is the number of times that cleaner fish $j$ in reef site $i$ 
chose the visitor over the resident; and $n=20$ (due to our choice of using 20 
choices per cleaner fish). By taking the natural logarithm and summing over all 
the cleaner fish and reef sites, we obtained the log-likelihood of the data 
given the model and parameters. We then proposed a new set of parameters drawn 
from a uniform distribution centred around the old parameter set. The amplitude 
of the uniform distribution used for each parameter can be found in Table 
\ref{tab:param}. Subsequently, we ran the model and calculated the likelihood 
with the new parameter set. We then used the ratio of the two likelihoods to 
choose which parameter set to keep. New parameter sets with a higher likelihood 
than the old set replaced old ones, and those with a lower likelihood replaced 
current ones  with a probability equal to the log-likelihood ratio. 
Given that we only used the likelihoods in the decision, we used an 
uninformative prior. Once we decided whether the new parameter set 
would replace the old one, we ran the model again to sample the likelihood 
distribution of the parameter set. We then started 
the cycle again by proposing a new set of parameters and repeated
the process for $1e^5$ steps. We ran 5 independent chains, 
discarded the first $1000$ samples of each chain as burn in, 
and after that, we kept 1 in every 100 samples to avoid autocorrelation. 
The collection of parameters sets kept in 
all chains approximates the posterior distribution. We coded the model 
as well as the fitting algorithm in *c++*, the diagnostics and visualization 
in R [@rcoreteam_Language_2021]. All codes are accessible at 
[![DOI](https://zenodo.org/badge/440585701.svg)](https://zenodo.org/badge/latestdoi/440585701).

@@

```{r rawdata,fig.cap='Relation between the response variable used in this study and the criteria used in previous studies to assess performance in the ephemeral reward task. In the x axis, we classified the performance of cleaner fish according to whether they developed a preference for the visitor in the initial round (initial only), in the initial and reversal (both), or none of them (none). In the y axis, we add the choices of two experimental sessions: in panel \\textbf{a} we use one session from the initial round and one from the reversal round when possible (as described in the main text); in panel \\textbf{b} we use two sessions from the initial round for all fish.',out.width='100%',fig.height=5,cache=FALSE}
plot_grid(initANDRev,init,ncol = 2,labels = c("a","b"),label_x = 0.15)
